Lightning Talk: Software Citation: Process, Principles, and Implementation

### 2016-08-12 meetings/WSSSPE4-lightning-talk/WSSSPE4-lightning-talk.tex
final adding copying and formatting authors and column lengths on last page

\usepackage[keeplastbox]{flushend} % equalizes columns on last page

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Daniel S. Katz\IEEEauthorrefmark{1},
Kyle E. Niemeyer\IEEEauthorrefmark{2},
Arfon M. Smith\IEEEauthorrefmark{3},
FORCE11 Software Citation Working Group\IEEEauthorrefmark{4}}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Illinois Urbana-Champaign\\
Urbana, Illinois, USA\\
Email: d.katz@ieee.org}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Oregon State University\\
Corvallis, Oregon, USA\\
Email: Kyle.Niemeyer@oregonstate.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}GitHub, Inc.\\
San Francisco, California, USA\\
Email: arfon@github.com}
\IEEEauthorblockA{\IEEEauthorrefmark{4}FORCE11\\
\url{https://www.force11.org/group/software-citation-working-group}}}

@@

@@

This presentation will discuss the principles (in brief: importance, credit and attribution, unique identification, persistence, accessibility, and specificity), how they will impact the practice of research, and they can be implemented by researchers, publishers, librarians and others who build and maintain repositories, scholars of science, university administrators, and research funders. It should also spark discussion in Track 2 of WSSSPE4 about both the next steps related to software citation and the community goals related to software credit, reproducibility, and sustainability.

>>>>

%\usepackage[keeplastbox]{flushend} % equalizes columns on last page

@@

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
\author{\IEEEauthorblockN{Daniel S. Katz\IEEEauthorrefmark{1},
Kyle E. Niemeyer\IEEEauthorrefmark{2},
Arfon M. Smith\IEEEauthorrefmark{3},
FORCE11 Software Citation Working Group\IEEEauthorrefmark{4}\\}
\vspace{0.2cm}
\IEEEauthorblockA{\IEEEauthorrefmark{1}University of Illinois Urbana-Champaign,
Urbana, Illinois, USA,
Email: d.katz@ieee.org}
\IEEEauthorblockA{\IEEEauthorrefmark{2}Oregon State University,
Corvallis, Oregon, USA,
Email: Kyle.Niemeyer@oregonstate.edu}
\IEEEauthorblockA{\IEEEauthorrefmark{3}GitHub, Inc.,
San Francisco, California, USA,
Email: arfon@github.com}
\IEEEauthorblockA{\IEEEauthorrefmark{4}FORCE11,
\url{https://www.force11.org/group/software-citation-working-group}}}

@@

\IEEEoverridecommandlockouts
\IEEEpubid{\makebox[\columnwidth]{This work is licensed under a \href{https://creativecommons.org/licenses/by/4.0/}{CC-BY-4.0 license}. \hfill} \hspace{\columnsep}\makebox[\columnwidth]{ }}

@@

{
This presentation will discuss the principles (in brief: importance, credit and attribution, unique identification, persistence, accessibility, and specificity), how they will impact the practice of research, and they can be implemented by researchers, publishers, librarians and others who build and maintain repositories, scholars of science, university administrators, and research funders. It should also spark discussion in Track 2 of WSSSPE4 about both the next steps related to software
\unskip\parfillskip 0pt \par }

\vfill \break

\noindent citation and the community goals related to software credit, reproducibility, and sustainability.
